---
title: "01. Data access"
author: Jessica Guezen
output: pdf_document
---

# Create temporary file directory
```{r}
outdir <- "~/Desktop/clim_land_arthropods"
dir.create(outdir)
```


# Climate Data

## Temperature
```{r}
outdir <- "~/Desktop/clim_land_arthropods/air_temp_2014"
dir.create(outdir)
file_name = file.path(outdir, "air_temp_2014.tar.gz")
url <- "http://climate.geog.udel.edu/html_pages/Global2014/air_temp_2014.tar.gz"
download.file(url, file_name)
untar(file_name, exdir = path.expand(outdir))
```


# Land-use and Arthropod Abundance Data

**** Download full dataset from Dryad: https://doi.org/10.5061/dryad.6tj407n (Martin, Emily A. et al. (2019). Data from: The interplay of landscape composition and configuration: new pathways to manage functional biodiversity and agro-ecosystem services across Europe [Dataset]. Dryad)

Save "Martin et al_2019_traits database_300319.xlsx" as CSV file "Trait_Data.csv" in temporary file directory (clim_land_arthropods):
- sheet = 1
- range = A4:K2087

Save "Martin et al_2019_data tables_300319.xlsx" as CSV file "Study_Metadata.csv" in temporary file directory (clim_land_arthropods):
- sheet = 1
- range = A4:M62

Save "Martin et al_2019_data tables_300319.xlsx" as CSV file "Site_Data.csv" in temporary file directory (clim_land_arthropods):
- sheet = 2
- range = A4:M2442

Save "Martin et al_2019_data tables_300319.xlsx" as CSV file "Species_Data.csv" in temporary file directory (clim_land_arthropods):
- sheet = 3
- range = A5:J35374

Save "Martin et al_2019_data tables_300319.xlsx" as CSV file "Landscape_Data.csv" in temporary file directory (clim_land_arthropods):
- sheet = 5
- range = A4:L10458
