---
title: "03. Data Cleaning"
author: Jessica Guezen
output: pdf_document
---

# Set up

Open CSVs:
```{r}
trait_dat = read.csv("~/Desktop/clim_land_arthropods/Trait_Data.csv",
                     header = TRUE)
species_dat = read.csv("~/Desktop/clim_land_arthropods/Species_Data.csv",
                       header = TRUE)
site_clim_dat = read.csv("~/Desktop/clim_land_arthropods/Site_Clim_Data.csv", header = TRUE)
land_dat = read.csv("~/Desktop/clim_land_arthropods/Landscape_Data.csv",
                    header = TRUE)
study_metdat = read.csv("~/Desktop/clim_land_arthropods/Study_Metadata.csv",
                        header = TRUE)
```

Load packages:
```{r}
library(tidyverse)
```

# Landscape Data

Change from long to wide format:
```{r}
land_dat_wide <-
  land_dat %>%
  pivot_wider(names_from = Radius_meters,
              names_sep = "_",
              values_from = c(Percent_seminatural,
                              Percent_arable,
                              Percent_forest,
                              Percent_urban,
                              Percent_water,
                              Total_Edge_density_kmperha,
                              Shannon_habitat_diversity_index))
rm(land_dat)
```

# Species, Trait, and Study Metadata

Remove all columns from study_metdat except Study.ID and Functional.groups:
```{r}
study_metdat <-
  study_metdat %>%
  dplyr::select(Study.ID, Functional.groups)
```

Get levels for Functional.groups:
```{r}
levels(as.factor(study_metdat$Functional.groups))
```

Add "Pollinator_study", "Pest_study", "Nat_enemy_study", and "Seed_pred_study" variables:
```{r}
study_metdat <-
  study_metdat %>%
  mutate(Pest_study = case_when(
    Functional.groups == "enemies, pests, pollinators" ~ 1,
    Functional.groups == "enemies, pollinators, pests" ~ 1,
    Functional.groups == "enemies, pests" ~ 1,
    Functional.groups == "pests" ~ 1,
    .default = 0))%>%
   mutate(Pollinator_study = case_when(
    Functional.groups == "enemies, pests, pollinators" ~ 1,
    Functional.groups == "enemies, pollinators, pests" ~ 1,
    Functional.groups == "pollinators" ~ 1,
    Functional.groups == "enemies, pollinators" ~ 1,
    .default = 0))%>%
  mutate(Nat_enemy_study = case_when(
    Functional.groups == "enemies"  ~ 1,
    Functional.groups == "enemies, pests, pollinators" ~ 1,
    Functional.groups == "enemies, pollinators, pests" ~ 1,
    Functional.groups == "enemies, pests" ~ 1,
    Functional.groups == "enemies, pollinators" ~ 1,
    .default = 0))%>%
  mutate(Seed_pred_study = case_when(
    Functional.groups == "seed predators"  ~ 1,
    .default = 0))
```

Combine species data and study metadata:
```{r}
species_dat <-
  species_dat %>%
  left_join(study_metdat,
            join_by(StudyID == Study.ID))
rm(study_metdat)
```

Check for duplicates in trait_dat:
```{r}
trait_dat$SpeciesID[duplicated(trait_dat$SpeciesID)]
```

Get levels for Functional_group when SpeciesID = "Syrphidae"
```{r}
trait_dat %>%
  filter(SpeciesID == "Syrphidae") %>%
  reframe(Functional_group)
```

Get levels for Functional_group when SpeciesID = "Diptera"
```{r}
trait_dat%>%
  filter(SpeciesID == "Diptera") %>%
  reframe(Functional_group)
```

Create new SpeciesID's based on Functional_group for Syrphidae and Diptera:
```{r}
trait_dat <-
  trait_dat %>%
  mutate(SpeciesID = 
           case_when(
             SpeciesID == "Syrphidae" & 
              Functional_group == "larval predator, adult pollinator" ~
               "Syrphidae_pred_poll",
             SpeciesID == "Syrphidae" & 
               Functional_group == "pollinator"~
               "Syrphidae_poll",
             SpeciesID == "Syrphidae" & 
               Functional_group == "predator"~
               "Syrphidae_pred",
             .default = SpeciesID
             ))%>%
  mutate(SpeciesID = 
           case_when(
             SpeciesID == "Diptera" & 
              Functional_group == "pollinator" ~
               "Diptera_poll",
             SpeciesID == "Diptera" & 
               Functional_group == "parasitoid of bees"~
               "Diptera_pred",
             .default = SpeciesID
             ))
```

Create new corrected_names based on Pollinator_study and Nat_Enemy_study for Syrphidae and Diptera:
```{r}
species_dat <-
  species_dat %>%
  mutate(corrected_name = 
           case_when(
             corrected_name == "Syrphidae" & 
              Pollinator_study == "1" & 
               Nat_enemy_study == "1" ~
               "Syrphidae_pred_poll",
             corrected_name == "Syrphidae" & 
               Pollinator_study == "1" & 
               Nat_enemy_study == "0" ~
               "Syrphidae_poll",
             corrected_name == "Syrphidae" & 
               Pollinator_study == "0" & 
               Nat_enemy_study == "1" ~
               "Syrphidae_pred",
             .default = corrected_name
             ))%>%
  mutate(corrected_name = 
           case_when(
             corrected_name == "Diptera" & 
               OrganismID == "Diptera sp. (trapnest parasitoid ie larva)" ~
               "Diptera_pred",
             corrected_name == "Diptera" & 
               OrganismID != "Diptera sp. (trapnest parasitoid ie larva)" ~
               "Diptera_poll",
             .default = corrected_name
             ))
```

Combine species and trait data:
```{r}
species_trait_dat <-
  species_dat %>%
  left_join(trait_dat,
            join_by(corrected_name == SpeciesID))
```

Remove Functional.groups variable:
```{r}
species_trait_dat <-
  species_trait_dat %>%
  dplyr::select(-Functional.groups)
```


# All data combined

Remove columns from site_clim_dat: X, Year, Site_description, Crop_species,
Tilling, Local_diversity, and Other_covariate:
```{r}
site_clim_dat <-
  site_clim_dat %>%
  dplyr::select(-X,
         -Year,
         -Site_description,
         -Crop_species,
         -Tilling,
         -Local_diversity,
         -Other_covariate)
```


```{r}
final_dat <-
  species_trait_dat %>%
  left_join(land_dat_wide,
            join_by(
              StudyID == StudyID,
              StudyID_yr == StudyID_yr,
              SiteID == SiteID))%>%
  left_join(site_clim_dat,
            join_by(
              StudyID == StudyID,
              StudyID_yr == StudyID_yr,
              SiteID == SiteID))
```


```{r}
levels(as.factor(final_dat$Functional_group))
```


Create functional group variables:
```{r}
final_dat <-
  final_dat %>%
  mutate(
    fg_pollinator = case_when(
      Functional_group ==
        "larval non-pest herbivore, adult pollinator" |
        Functional_group ==
        "larval parasitoid, adult pollinator" |
        Functional_group ==
        "larval parasitoid, adult pollinator (larva)" |
        Functional_group ==
        "larval pest herbivore, adult pollinator" |
        Functional_group ==
        "larval pest herbivore, adult pollinator (adults)" |
        Functional_group ==
        "larval predator, adult pollinator" |
        Functional_group ==
        "pollinator" ~ 1,
      .default = 0
    ),
    fg_nat_enemy = case_when(
      Functional_group ==
        "aphid-tender, predator" |
        Functional_group ==
        "cleptoparasite"  |
        Functional_group ==
        "larval parasitoid, adult pollinator" |
        Functional_group ==
        "larval parasitoid, adult pollinator (larva)" |
        Functional_group ==
        "larval predator, adult pollinator" |
        Functional_group ==
        "parasitoid" |
        Functional_group ==
        "parasitoid of bees" |
        Functional_group ==
        "predator" ~ 1,
      .default = 0
    ),
    fg_pest = case_when(
      Functional_group ==
        "larval pest herbivore, adult pollinator" |
        Functional_group ==
        "larval pest herbivore, adult pollinator (adults)"  |
        Functional_group ==
        "pest herbivore" ~ 1,
      .default = 0
    )
  )
```

```{r}
levels(as.factor(final_dat$diet_breadth))
levels(as.factor(final_dat$overwintering_habitat))
levels(as.factor(final_dat$dispersal))
```

```{r}
sum(is.na(final_dat$diet_breadth))
sum(is.na(final_dat$overwintering_habitat))
sum(is.na(final_dat$dispersal))
```

```{r}
final_dat %>%
  filter(Pollinator_study == 1) %>%
  count(diet_breadth, dispersal, overwintering_habitat) 
```

```{r}
final_dat %>%
  filter(Pest_study == 1) %>%
  count(diet_breadth, dispersal, overwintering_habitat) 
```

```{r}
final_dat %>%
  filter(Nat_enemy_study == 1) %>%
  count(diet_breadth, dispersal, overwintering_habitat) 
```

Create trait syndrome (ts) variables for pollinators:
```{r}
final_dat <-
  final_dat %>%
  mutate(
    #TS1
    ts_poll_gen_flight_noncrop = case_when(
      fg_pollinator == 1 &
      diet_breadth == "generalist" &
      dispersal == "flight" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS2
    ts_poll_gen_flight_crop = case_when(
      fg_pollinator == 1 &
      diet_breadth == "generalist" &
      dispersal == "flight" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS3
    ts_poll_gen_flightwind_noncrop = case_when(
      fg_pollinator == 1 &
      diet_breadth == "generalist" &
      dispersal == "flightwind" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS4
    ts_poll_gen_flightwind_crop = case_when(
      fg_pollinator == 1 &
      diet_breadth == "generalist" &
      dispersal == "flightwind" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS5
    ts_poll_gen_ground_noncrop = case_when(
      fg_pollinator == 1 &
      diet_breadth == "generalist" &
      dispersal == "ground" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS6
    ts_poll_gen_ground_crop = case_when(
      fg_pollinator == 1 &
      diet_breadth == "generalist" &
      dispersal == "ground" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS7
    ts_poll_gen_wind_noncrop = case_when(
      fg_pollinator == 1 &
      diet_breadth == "generalist" &
      dispersal == "wind" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS8
    ts_poll_gen_wind_crop = case_when(
      fg_pollinator == 1 &
      diet_breadth == "generalist" &
      dispersal == "wind" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS9
    ts_poll_spec_flight_noncrop = case_when(
      fg_pollinator == 1 &
      diet_breadth == "specialist" &
      dispersal == "flight" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS10
    ts_poll_spec_flight_crop = case_when(
      fg_pollinator == 1 &
      diet_breadth == "specialist" &
      dispersal == "flight" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS11
    ts_poll_spec_flightwind_noncrop = case_when(
      fg_pollinator == 1 &
      diet_breadth == "specialist" &
      dispersal == "flight/wind" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS12
    ts_poll_spec_flightwind_crop = case_when(
      fg_pollinator == 1 &
      diet_breadth == "specialist" &
      dispersal == "flight/wind" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS13
    ts_poll_spec_ground_noncrop = case_when(
      fg_pollinator == 1 &
      diet_breadth == "specialist" &
      dispersal == "ground" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS14
    ts_poll_spec_wind_noncrop = case_when(
      fg_pollinator == 1 &
      diet_breadth == "specialist" &
      dispersal == "wind" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    )
  )
```

Create trait syndrome (ts) variables for natural enemies:
```{r}
final_dat <-
  final_dat %>%
  mutate(
    #TS1
    ts_nat_gen_flight_noncrop = case_when(
      fg_nat_enemy == 1 &
      diet_breadth == "generalist" &
      dispersal == "flight" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS2
    ts_nat_gen_flight_crop = case_when(
      fg_nat_enemy == 1 &
      diet_breadth == "generalist" &
      dispersal == "flight" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS3
    ts_nat_gen_flightwind_noncrop = case_when(
      fg_nat_enemy == 1 &
      diet_breadth == "generalist" &
      dispersal == "flightwind" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS4
    ts_nat_gen_flightwind_crop = case_when(
      fg_nat_enemy == 1 &
      diet_breadth == "generalist" &
      dispersal == "flightwind" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS5
    ts_nat_gen_ground_noncrop = case_when(
      fg_nat_enemy == 1 &
      diet_breadth == "generalist" &
      dispersal == "ground" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS6
    ts_nat_gen_ground_crop = case_when(
      fg_nat_enemy == 1 &
      diet_breadth == "generalist" &
      dispersal == "ground" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS7
    ts_nat_gen_wind_noncrop = case_when(
      fg_nat_enemy == 1 &
      diet_breadth == "generalist" &
      dispersal == "wind" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS8
    ts_nat_gen_wind_crop = case_when(
      fg_nat_enemy == 1 &
      diet_breadth == "generalist" &
      dispersal == "wind" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS9
    ts_nat_spec_flight_noncrop = case_when(
      fg_nat_enemy == 1 &
      diet_breadth == "specialist" &
      dispersal == "flight" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS10
    ts_nat_spec_flight_crop = case_when(
      fg_nat_enemy == 1 &
      diet_breadth == "specialist" &
      dispersal == "flight" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS11
    ts_nat_spec_flightwind_noncrop = case_when(
      fg_nat_enemy == 1 &
      diet_breadth == "specialist" &
      dispersal == "flight/wind" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS12
    ts_nat_spec_flightwind_crop = case_when(
      fg_nat_enemy == 1 &
      diet_breadth == "specialist" &
      dispersal == "flight/wind" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS13
    ts_nat_spec_ground_noncrop = case_when(
      fg_nat_enemy == 1 &
      diet_breadth == "specialist" &
      dispersal == "ground" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS14
    ts_nat_spec_wind_noncrop = case_when(
      fg_nat_enemy == 1 &
      diet_breadth == "specialist" &
      dispersal == "wind" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    )
  )
```

Create trait syndrome (ts) variables for pests:
```{r}
final_dat <-
  final_dat %>%
  mutate(
    #TS1
    ts_pest_gen_flight_noncrop = case_when(
      fg_pest == 1 &
      diet_breadth == "generalist" &
      dispersal == "flight" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS2
    ts_pest_gen_flight_crop = case_when(
      fg_pest == 1 &
      diet_breadth == "generalist" &
      dispersal == "flight" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS3
    ts_pest_gen_flightwind_noncrop = case_when(
      fg_pest == 1 &
      diet_breadth == "generalist" &
      dispersal == "flightwind" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS4
    ts_pest_gen_flightwind_crop = case_when(
      fg_pest == 1 &
      diet_breadth == "generalist" &
      dispersal == "flightwind" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS5
    ts_pest_gen_ground_noncrop = case_when(
      fg_pest == 1 &
      diet_breadth == "generalist" &
      dispersal == "ground" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS6
    ts_pest_gen_ground_crop = case_when(
      fg_pest == 1 &
      diet_breadth == "generalist" &
      dispersal == "ground" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS7
    ts_pest_gen_wind_noncrop = case_when(
      fg_pest == 1 &
      diet_breadth == "generalist" &
      dispersal == "wind" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS8
    ts_pest_gen_wind_crop = case_when(
      fg_pest == 1 &
      diet_breadth == "generalist" &
      dispersal == "wind" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS9
    ts_pest_spec_flight_noncrop = case_when(
      fg_pest == 1 &
      diet_breadth == "specialist" &
      dispersal == "flight" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS10
    ts_pest_spec_flight_crop = case_when(
      fg_pest == 1 &
      diet_breadth == "specialist" &
      dispersal == "flight" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS11
    ts_pest_spec_flightwind_noncrop = case_when(
      fg_pest == 1 &
      diet_breadth == "specialist" &
      dispersal == "flight/wind" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS12
    ts_pest_spec_flightwind_crop = case_when(
      fg_pest == 1 &
      diet_breadth == "specialist" &
      dispersal == "flight/wind" &
        overwintering_habitat == "natural, margin, crop" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS13
    ts_pest_spec_ground_noncrop = case_when(
      fg_pest == 1 &
      diet_breadth == "specialist" &
      dispersal == "ground" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    ),
    #TS14
    ts_pest_spec_wind_noncrop = case_when(
      fg_pest == 1 &
      diet_breadth == "specialist" &
      dispersal == "wind" &
        overwintering_habitat == "natural, margin" ~ 1,
      is.na(diet_breadth) | 
        is.na(dispersal) | 
        is.na(overwintering_habitat) ~ NA,
      .default = 0
    )
  )
```

# Final data cleaning

Remove organic sites:
```{r}
final_dat <-
  final_dat %>%
  filter(!Management == "organic")%>%
  dplyr::select(-Management)
```

Calculate abundance and sampling effort: 
```{r}
final_dat <-
  final_dat %>%
  group_by(StudyID,
           Year,
           SiteID,
           Sampling_method,
           Block)%>%
  mutate(total_abund = sum(Abundance),
         #pollinator TS:
         ts_poll_gen_flight_noncrop_abund = 
           sum(ts_poll_gen_flight_noncrop*Abundance),
         ts_poll_gen_flight_crop_abund = 
           sum(ts_poll_gen_flight_crop*Abundance),
         ts_poll_gen_flightwind_noncrop_abund = 
           sum(ts_poll_gen_flightwind_noncrop*Abundance),
         ts_poll_gen_flightwind_crop_abund = 
           sum(ts_poll_gen_flightwind_crop*Abundance),
         ts_poll_gen_ground_noncrop_abund = 
           sum(ts_poll_gen_ground_noncrop*Abundance),
         ts_poll_gen_ground_crop_abund = 
           sum(ts_poll_gen_ground_crop*Abundance),
         ts_poll_gen_wind_noncrop_abund = 
           sum(ts_poll_gen_wind_noncrop*Abundance),
         ts_poll_gen_wind_crop_abund = 
           sum(ts_poll_gen_wind_crop*Abundance),
         ts_poll_spec_flight_noncrop_abund = 
           sum(ts_poll_spec_flight_noncrop*Abundance),
         ts_poll_spec_flight_crop_abund = 
           sum(ts_poll_spec_flight_crop*Abundance),
         ts_poll_spec_flightwind_noncrop_abund = 
           sum(ts_poll_spec_flightwind_noncrop*Abundance),
         ts_poll_spec_flightwind_crop_abund = 
           sum(ts_poll_spec_flightwind_crop*Abundance),
         ts_poll_spec_ground_noncrop_abund = 
           sum(ts_poll_spec_ground_noncrop*Abundance),
         ts_poll_spec_wind_noncrop_abund = 
           sum(ts_poll_spec_wind_noncrop*Abundance),
         #Natural enemy TS:
         ts_nat_gen_flight_noncrop_abund = 
           sum(ts_nat_gen_flight_noncrop*Abundance),
         ts_nat_gen_flight_crop_abund = 
           sum(ts_nat_gen_flight_crop*Abundance),
         ts_nat_gen_flightwind_noncrop_abund = 
           sum(ts_nat_gen_flightwind_noncrop*Abundance),
         ts_nat_gen_flightwind_crop_abund = 
           sum(ts_nat_gen_flightwind_crop*Abundance),
         ts_nat_gen_ground_noncrop_abund = 
           sum(ts_nat_gen_ground_noncrop*Abundance),
         ts_nat_gen_ground_crop_abund = 
           sum(ts_nat_gen_ground_crop*Abundance),
         ts_nat_gen_wind_noncrop_abund = 
           sum(ts_nat_gen_wind_noncrop*Abundance),
         ts_nat_gen_wind_crop_abund = 
           sum(ts_nat_gen_wind_crop*Abundance),
         ts_nat_spec_flight_noncrop_abund = 
           sum(ts_nat_spec_flight_noncrop*Abundance),
         ts_nat_spec_flight_crop_abund = 
           sum(ts_nat_spec_flight_crop*Abundance),
         ts_nat_spec_flightwind_noncrop_abund = 
           sum(ts_nat_spec_flightwind_noncrop*Abundance),
         ts_nat_spec_flightwind_crop_abund = 
           sum(ts_nat_spec_flightwind_crop*Abundance),
         ts_nat_spec_ground_noncrop_abund = 
           sum(ts_nat_spec_ground_noncrop*Abundance),
         ts_nat_spec_wind_noncrop_abund = 
           sum(ts_nat_spec_wind_noncrop*Abundance),
         #Pest TS:
         ts_pest_gen_flight_noncrop_abund = 
           sum(ts_pest_gen_flight_noncrop*Abundance),
         ts_pest_gen_flight_crop_abund = 
           sum(ts_pest_gen_flight_crop*Abundance),
         ts_pest_gen_flightwind_noncrop_abund = 
           sum(ts_pest_gen_flightwind_noncrop*Abundance),
         ts_pest_gen_flightwind_crop_abund = 
           sum(ts_pest_gen_flightwind_crop*Abundance),
         ts_pest_gen_ground_noncrop_abund = 
           sum(ts_pest_gen_ground_noncrop*Abundance),
         ts_pest_gen_ground_crop_abund = 
           sum(ts_pest_gen_ground_crop*Abundance),
         ts_pest_gen_wind_noncrop_abund = 
           sum(ts_pest_gen_wind_noncrop*Abundance),
         ts_pest_gen_wind_crop_abund = 
           sum(ts_pest_gen_wind_crop*Abundance),
         ts_pest_spec_flight_noncrop_abund = 
           sum(ts_pest_spec_flight_noncrop*Abundance),
         ts_pest_spec_flight_crop_abund = 
           sum(ts_pest_spec_flight_crop*Abundance),
         ts_pest_spec_flightwind_noncrop_abund = 
           sum(ts_pest_spec_flightwind_noncrop*Abundance),
         ts_pest_spec_flightwind_crop_abund = 
           sum(ts_pest_spec_flightwind_crop*Abundance),
         ts_pest_spec_ground_noncrop_abund = 
           sum(ts_pest_spec_ground_noncrop*Abundance),
         ts_pest_spec_wind_noncrop_abund = 
           sum(ts_pest_spec_wind_noncrop*Abundance),
         #Functional groups:
         fg_pollinator_abund = 
           sum(fg_pollinator*Abundance),
         fg_nat_enemy_abund = 
           sum(fg_nat_enemy*Abundance),
         fg_pest_abund = 
           sum(fg_pest*Abundance))%>%
  dplyr::select(-corrected_name,
         -OrganismID,
         -Abundance,
         -Authority,
         -Family,
         -Taxonomic_group,
         -Functional_group,
         -diet_breadth,
         -agricultural_specialist,
         -diet_life_history,
         -overwintering_habitat,
         -dispersal,
         -stratum,
         -ts_poll_gen_flight_noncrop,
         -ts_poll_gen_flight_crop,
         -ts_poll_gen_flightwind_noncrop,
         -ts_poll_gen_flightwind_crop,
         -ts_poll_gen_ground_noncrop,
         -ts_poll_gen_ground_crop,
         -ts_poll_gen_wind_noncrop,
         -ts_poll_gen_wind_crop,
         -ts_poll_spec_flight_noncrop,
         -ts_poll_spec_flight_crop,
         -ts_poll_spec_flightwind_noncrop,
         -ts_poll_spec_flightwind_crop,
         -ts_poll_spec_ground_noncrop,
         -ts_poll_spec_wind_noncrop,
         -ts_nat_gen_flight_noncrop,
         -ts_nat_gen_flight_crop,
         -ts_nat_gen_flightwind_noncrop,
         -ts_nat_gen_flightwind_crop,
         -ts_nat_gen_ground_noncrop,
         -ts_nat_gen_ground_crop,
         -ts_nat_gen_wind_noncrop,
         -ts_nat_gen_wind_crop,
         -ts_nat_spec_flight_noncrop,
         -ts_nat_spec_flight_crop,
         -ts_nat_spec_flightwind_noncrop,
         -ts_nat_spec_flightwind_crop,
         -ts_nat_spec_ground_noncrop,
         -ts_nat_spec_wind_noncrop,
         -ts_pest_gen_flight_noncrop,
         -ts_pest_gen_flight_crop,
         -ts_pest_gen_flightwind_noncrop,
         -ts_pest_gen_flightwind_crop,
         -ts_pest_gen_ground_noncrop,
         -ts_pest_gen_ground_crop,
         -ts_pest_gen_wind_noncrop,
         -ts_pest_gen_wind_crop,
         -ts_pest_spec_flight_noncrop,
         -ts_pest_spec_flight_crop,
         -ts_pest_spec_flightwind_noncrop,
         -ts_pest_spec_flightwind_crop,
         -ts_pest_spec_ground_noncrop,
         -ts_pest_spec_wind_noncrop,
         -fg_pollinator,
         -fg_nat_enemy,
         -fg_pest) %>%
  distinct(.keep_all = TRUE) %>%
  ungroup()%>%
  mutate(sampling_effort =
           case_when(
             Abundance_duration > 0 & Nb_censuses > 0 ~
               Abundance_duration*Nb_censuses,
             Abundance_duration > 0 & Nb_censuses == 0 ~
               Abundance_duration,
             Abundance_duration == 0 & Nb_censuses > 0 ~
               Nb_censuses,
             Abundance_duration > 0 & is.na(Nb_censuses) ~
               Abundance_duration,
             is.na(Abundance_duration) & Nb_censuses > 0 ~
               Nb_censuses
             ))
```

Calculate abundances scaled by sampling effort:
```{r}
final_dat <-
  final_dat %>%
  group_by(StudyID,
           Year) %>%
  mutate(sampling_effort_scaled = sampling_effort / max(sampling_effort)) %>%
  ungroup() %>%
  mutate(
    total_abund_scaled = total_abund / sampling_effort_scaled,
    ts_poll_gen_flight_noncrop_abund_scaled =
      ts_poll_gen_flight_noncrop_abund / sampling_effort_scaled,
    ts_poll_gen_flight_crop_abund_scaled =
      ts_poll_gen_flight_crop_abund / sampling_effort_scaled,
    ts_poll_gen_flightwind_noncrop_abund_scaled =
      ts_poll_gen_flightwind_noncrop_abund / sampling_effort_scaled,
    ts_poll_gen_flightwind_crop_abund_scaled =
      ts_poll_gen_flightwind_crop_abund / sampling_effort_scaled,
    ts_poll_gen_ground_noncrop_abund_scaled =
      ts_poll_gen_ground_noncrop_abund / sampling_effort_scaled,
    ts_poll_gen_ground_crop_abund_scaled =
      ts_poll_gen_ground_crop_abund / sampling_effort_scaled,
    ts_poll_gen_wind_noncrop_abund_scaled =
      ts_poll_gen_wind_noncrop_abund / sampling_effort_scaled,
    ts_poll_gen_wind_crop_abund_scaled =
      ts_poll_gen_wind_crop_abund / sampling_effort_scaled,
    ts_poll_spec_flight_noncrop_abund_scaled =
      ts_poll_spec_flight_noncrop_abund / sampling_effort_scaled,
    ts_poll_spec_flight_crop_abund_scaled =
      ts_poll_spec_flight_crop_abund / sampling_effort_scaled,
    ts_poll_spec_flightwind_noncrop_abund_scaled =
      ts_poll_spec_flightwind_noncrop_abund / sampling_effort_scaled,
    ts_poll_spec_flightwind_crop_abund_scaled =
      ts_poll_spec_flightwind_crop_abund / sampling_effort_scaled,
    ts_poll_spec_ground_noncrop_abund_scaled =
      ts_poll_spec_ground_noncrop_abund / sampling_effort_scaled,
    ts_poll_spec_wind_noncrop_abund_scaled =
      ts_poll_spec_wind_noncrop_abund / sampling_effort_scaled,
    ts_nat_gen_flight_noncrop_abund_scaled =
      ts_nat_gen_flight_noncrop_abund / sampling_effort_scaled,
    ts_nat_gen_flight_crop_abund_scaled =
      ts_nat_gen_flight_crop_abund / sampling_effort_scaled,
    ts_nat_gen_flightwind_noncrop_abund_scaled =
      ts_nat_gen_flightwind_noncrop_abund / sampling_effort_scaled,
    ts_nat_gen_flightwind_crop_abund_scaled =
      ts_nat_gen_flightwind_crop_abund / sampling_effort_scaled,
    ts_nat_gen_ground_noncrop_abund_scaled =
      ts_nat_gen_ground_noncrop_abund / sampling_effort_scaled,
    ts_nat_gen_ground_crop_abund_scaled =
      ts_nat_gen_ground_crop_abund / sampling_effort_scaled,
    ts_nat_gen_wind_noncrop_abund_scaled =
      ts_nat_gen_wind_noncrop_abund / sampling_effort_scaled,
    ts_nat_gen_wind_crop_abund_scaled =
      ts_nat_gen_wind_crop_abund / sampling_effort_scaled,
    ts_nat_spec_flight_noncrop_abund_scaled =
      ts_nat_spec_flight_noncrop_abund / sampling_effort_scaled,
    ts_nat_spec_flight_crop_abund_scaled =
      ts_nat_spec_flight_crop_abund / sampling_effort_scaled,
    ts_nat_spec_flightwind_noncrop_abund_scaled =
      ts_nat_spec_flightwind_noncrop_abund / sampling_effort_scaled,
    ts_nat_spec_flightwind_crop_abund_scaled =
      ts_nat_spec_flightwind_crop_abund / sampling_effort_scaled,
    ts_nat_spec_ground_noncrop_abund_scaled =
      ts_nat_spec_ground_noncrop_abund / sampling_effort_scaled,
    ts_nat_spec_wind_noncrop_abund_scaled =
      ts_nat_spec_wind_noncrop_abund / sampling_effort_scaled,
    ts_pest_gen_flight_noncrop_abund_scaled =
      ts_pest_gen_flight_noncrop_abund / sampling_effort_scaled,
    ts_pest_gen_flight_crop_abund_scaled =
      ts_pest_gen_flight_crop_abund / sampling_effort_scaled,
    ts_pest_gen_flightwind_noncrop_abund_scaled =
      ts_pest_gen_flightwind_noncrop_abund / sampling_effort_scaled,
    ts_pest_gen_flightwind_crop_abund_scaled =
      ts_pest_gen_flightwind_crop_abund / sampling_effort_scaled,
    ts_pest_gen_ground_noncrop_abund_scaled =
      ts_pest_gen_ground_noncrop_abund / sampling_effort_scaled,
    ts_pest_gen_ground_crop_abund_scaled =
      ts_pest_gen_ground_crop_abund / sampling_effort_scaled,
    ts_pest_gen_wind_noncrop_abund_scaled =
      ts_pest_gen_wind_noncrop_abund / sampling_effort_scaled,
    ts_pest_gen_wind_crop_abund_scaled =
      ts_pest_gen_wind_crop_abund / sampling_effort_scaled,
    ts_pest_spec_flight_noncrop_abund_scaled =
      ts_pest_spec_flight_noncrop_abund / sampling_effort_scaled,
    ts_pest_spec_flight_crop_abund_scaled =
      ts_pest_spec_flight_crop_abund / sampling_effort_scaled,
    ts_pest_spec_flightwind_noncrop_abund_scaled =
      ts_pest_spec_flightwind_noncrop_abund / sampling_effort_scaled,
    ts_pest_spec_flightwind_crop_abund_scaled =
      ts_pest_spec_flightwind_crop_abund / sampling_effort_scaled,
    ts_pest_spec_ground_noncrop_abund_scaled =
      ts_pest_spec_ground_noncrop_abund / sampling_effort_scaled,
    ts_pest_spec_wind_noncrop_abund_scaled =
      ts_pest_spec_wind_noncrop_abund / sampling_effort_scaled,
    fg_pollinator_abund_scaled =
      fg_pollinator_abund / sampling_effort_scaled,
    fg_nat_enemy_abund_scaled =
      fg_nat_enemy_abund / sampling_effort_scaled,
    fg_pest_abund_scaled =
      fg_pest_abund / sampling_effort_scaled
  )
```

Rename variables:
```{r}
final_dat <-
  final_dat %>%
  rename(
    c(
      semi_100 = Percent_seminatural_100,
      semi_250 = Percent_seminatural_250,
      semi_500 = Percent_seminatural_500,
      semi_1000 = Percent_seminatural_1000,
      semi_2000 = Percent_seminatural_2000,
      semi_3000 = Percent_seminatural_3000,
      arable_100 = Percent_arable_100,
      arable_250 = Percent_arable_250,
      arable_500 = Percent_arable_500,
      arable_1000 = Percent_arable_1000,
      arable_2000 = Percent_arable_2000,
      arable_3000 = Percent_arable_3000,
      edge_100 = Total_Edge_density_kmperha_100,
      edge_250 = Total_Edge_density_kmperha_250,
      edge_500 = Total_Edge_density_kmperha_500,
      edge_1000 = Total_Edge_density_kmperha_1000,
      edge_2000 = Total_Edge_density_kmperha_2000,
      edge_3000 = Total_Edge_density_kmperha_3000
    )
  )
```

Calculate climate variables:
```{r}
final_dat <-
  final_dat %>%
  rowwise() %>%
  mutate(
    TAP = sum(
      Jan_precip,
      Feb_precip,
      Mar_precip,
      Apr_precip,
      May_precip,
      Jun_precip,
      Jul_precip,
      Aug_precip,
      Sep_precip,
      Oct_precip,
      Nov_precip,
      Dec_precip
    ),
    min_precip = min(
      Jan_precip,
      Feb_precip,
      Mar_precip,
      Apr_precip,
      May_precip,
      Jun_precip,
      Jul_precip,
      Aug_precip,
      Sep_precip,
      Oct_precip,
      Nov_precip,
      Dec_precip
    ),
    max_precip = max(
      Jan_precip,
      Feb_precip,
      Mar_precip,
      Apr_precip,
      May_precip,
      Jun_precip,
      Jul_precip,
      Aug_precip,
      Sep_precip,
      Oct_precip,
      Nov_precip,
      Dec_precip
    ),
    MAT = mean(
      c(
        Jan_temp,
        Feb_temp,
        Mar_temp,
        Apr_temp,
        May_temp,
        Jun_temp,
        Jul_temp,
        Aug_temp,
        Sep_temp,
        Oct_temp,
        Nov_temp,
        Dec_temp
      )
    ),
    min_temp = min(
      c(
        Jan_temp,
        Feb_temp,
        Mar_temp,
        Apr_temp,
        May_temp,
        Jun_temp,
        Jul_temp,
        Aug_temp,
        Sep_temp,
        Oct_temp,
        Nov_temp,
        Dec_temp
      )
    ),
    max_temp = max(
      c(
        Jan_temp,
        Feb_temp,
        Mar_temp,
        Apr_temp,
        May_temp,
        Jun_temp,
        Jul_temp,
        Aug_temp,
        Sep_temp,
        Oct_temp,
        Nov_temp,
        Dec_temp
      )
    )
  )
```

Change temperatures from C to K:
```{r}
library(weathermetrics)
final_dat <-
  final_dat %>%
  mutate(
    MAT = celsius.to.kelvin(MAT),
    min_temp = celsius.to.kelvin(min_temp),
    max_temp = celsius.to.kelvin(max_temp)
  )
```

Add site data:
```{r}
site_dat = read.csv("~/Desktop/PhD/Chapter 1/Data/Working/R/Site_Data.csv",
                    header = TRUE)
```

```{r}
final_dat <-
  final_dat %>%
  left_join(site_dat,
            join_by(StudyID_yr == StudyID_yr,
                    Block == Block,
                    SiteID == SiteID))
```

# Write CSV

```{r}
write.csv(final_dat, "~/Desktop/clim_land_arthropods/final_dat.csv")
```
